Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-02-19 ms_pre_post.Rmd
Revise first paragraph

Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009]. Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple reproductive decisions [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012]. From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), and by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance). Evolution of post-copulatory inbreeding avoidance requires that females are polyandrous, defined as mating with multiple males during a single reproductive bout. Further, such polyandry might itself be under selection because given inbreeding depression it allows females to mate with additional unrelated males following an initial mating with a relative, thereby facilitating pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation (i.e., given a 'fair raffle' among sperm provided by females' mates). Polyandry can thereby simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice. Polyandry, which might not increase female reproductive success and therefore requires explanation [@Parker2013], has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002]. However, there is surprisingly little theory or modelling that critically examines such widely-invoked hypotheses, and hence examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or how evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.

>>>>

Inbreeding, defined as reproduction between relatives, often greatly reduces the fitness of resulting inbred offspring [termed 'inbreeding depression'; @Charlesworth1999; @Keller2002; @Charlesworth2009]. Such strong inbreeding depression is widely hypothesised to drive evolution of inbreeding avoidance, which can be enacted through multiple interacting reproductive strategies [@Parker1979; @Parker2006; @Pusey1996; @Szulkin2012]. From the perspective of a focal breeding female, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males after mating has occurred (i.e., post-copulatory inbreeding avoidance). Evolution of post-copulatory inbreeding avoidance requires that females express some non-trivial degree of polyandry, defined as mating with multiple males during a single reproductive bout. Further, given inbreeding depression, such polyandry might itself be under selection and evolve if it allows females to mate with additional unrelated males following an initial mating with a relative. Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm provided by females' mates (i.e., 'fair raffle'). Overall, polyandry can therefore simultaneously allow females to mate with less closely related males and create the opportunity for further inbreeding avoidance enacted through active post-copulatory choice, and has consequently been widely hypothesised to evolve as an adaptation to allow females to avoid inbreeding and thereby increase offspring fitness [@Zeh1997; @Jennions2000; @Tregenza2002]. Resulting indirect selection on polyandry could explain its evolution in cases where multiple mating does not increase female reproductive success, or even where polyandry reduces reproductive success and therefore imposes direct fitness costs to polyandrous females. However, despite such widely-invoked hypotheses, there is surprising little theory or modelling that critically examines the conditions under which pre-copulatory or post-copulatory inbreeding avoidance, or both strategies, are predicted to evolve, or that examines how the evolution of such strategies of inbreeding avoidance might feed back to affect underlying evolution of polyandry.

<!--- XXX XXX XXX LEFT OFF HERE XXX XXX XXX --->

<!--- Something seems redundant about ''sperm provided by females' mates''. This is probably okay though  --->
<!--- I think I know what you mean, but is there any reason not to be bolder than 'help explain'? Could it not entirely explain most or all of the reason for selection for polyandry in some cases? --->
<!--- I've left out survival, as decreased survival isn't really a cost unless it reduces reproductive success --->
<!--- Parker and Birkhead (2013) was cited to identify the problem of polyandry, but I've removed it here because they don't really discuss inbreeding, and there wasn't really a good way to cite them here given the edits to the text. --->
